Simulation

### 2022-10-15 Quarto_Simulation/index.qmd
Fixed some file naming issues.
Make the html document nicer.

---
title: "Simulation"
author: "Jeremy Selva"
format: html
---

@@

```{r Save Simulated Data Saturated}
saveRDS(saturation_simulated_database, 
        file = "saturated_simulated_database.rds")
```

>>>>

---
title: "Simulation"
author: "Jeremy Selva"
format:
  html:
    theme: 
      light: cerulean 
      dark: cyborg
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: false
    code-fold: show
    code-overflow: scroll
    code-copy: true
    code-tools: true
    code-link: true
    self-contained: false
    smooth-scroll: true
execute: 
  cache: true
---

@@

```{r Save Simulated Data Saturated}
saveRDS(saturation_simulated_database, 
        file = "saturation_simulated_database.rds")
```
